---
title: "Weight of Fish"
author: "Emraida Ortanez"
date: "October 28, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch Model

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!--> 

```{r}
# read in the fish data
fishdata <- read.csv(file="Fish.csv",header = TRUE )
PerchData <- filter(fishdata,Species=="Perch") %>% select(-Species)
```
Now Build our Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = PerchData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
### The best two regressor model for Perch is Height and Width. This is also the best overall model as measured by adjusted R-Squared
  

# Bream Model 
<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
```{r}
# read in the fish data
fishdata <- read.csv(file="Fish.csv",header = TRUE )
BreamData <- filter(fishdata,Species=="Bream") %>% select(-Species)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = BreamData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
### The best two regressor model for Bream is Height and then L2- Height. So we can see the the adjusted R squared is 0.9356 for Length 2-Height.  
  
# Smelt Model
```{r}
# read in the fish data
fishdata <- read.csv(file="Fish.csv",header = TRUE )
SmeltData <- filter(fishdata,Species=="Smelt") %>% select(-Species)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = SmeltData,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
### For the Smelt  Model the best  regressor model is L2 and width, The best overall model for regressor includes L1 L2 Height and Weight   
    
# Discussion and Final Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
### Based on the information we have, we can say that we found out two different variables for each fish regression model. To explain the two-element regression model's best explanation is to describe the weight of the fish. For perch, it was Height and Width. For Bream, it was Length and Width. For Smelt, it was L2 and Height. For each different fish, the best two-element regression model are different. One id Height and Width. The other is Length and Width, and one is Lenght and Height  
    
